Abb Analysis

### 2017-02-16 abbDataAnalysis_Script.Rmd
prepare for the analysis object export

  mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
                        sub.mrkt+as.factor(host.type)+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        sub.mrkt+as.factor(host.type)+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
```

  mod.ext.str <- lm(str.ext.prem~type+as.factor(bedbath),
                    data=str.data.ic)
  mod.pot.str <- lm(str.pot.prem~type+as.factor(bedbath),
                    data=str.data.ic)

@@

  mod.ext.host.prem <- lm(str.ext.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
```

@@

  mod.ext.ps <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[ps,])

  mod.ext.os <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[os,])

  mod.ext.mu <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[mu,])

  mod.ext.un <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[un,])

@@

pra.coef <- extrMWLCoef(pot.results.all,
                        est.points,
                        x.names)
era.coef <- extrMWLCoef(ext.results.all,
                        est.points,
                        x.names)
prp.coef <- extrMWLCoef(pot.results.ps,
                        est.points,
                        x.names)
pro.coef <- extrMWLCoef(pot.results.os,
                        est.points,
                        x.names)
prm.coef <- extrMWLCoef(pot.results.mu,
                        est.points,
                        x.names)
pru.coef <- extrMWLCoef(pot.results.un,
                        est.points,
                        x.names)
erp.coef <- extrMWLCoef(ext.results.ps,
                        est.points,
                        x.names)
ero.coef <- extrMWLCoef(ext.results.os,
                        est.points,
                        x.names)
erm.coef <- extrMWLCoef(ext.results.mu,
                        est.points,
                        x.names)
eru.coef <- extrMWLCoef(ext.results.un,
                        est.points,
                        x.names)
```

@@

erp.surfs <- makeMWLSurfs(erp.coef,
                          est.points)
ero.surfs <- makeMWLSurfs(ero.coef,
                          est.points)
erm.surfs <- makeMWLSurfs(erm.coef,
                          est.points)
eru.surfs <- makeMWLSurfs(eru.coef,
                          est.points)

>>>>

  mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
                        sub.mrkt+as.factor(host.type)+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        sub.mrkt+as.factor(host.type)+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)

  pref.models <- list(mod.ext.str, mod.ext.loc, mod.ext.host, 
                      mod.pot.str, mod.pot.loc, mod.pot.host)
  names(pref.models) <- c('ext.str', 'ext.loc', 'ext.host',
                          'pot.str', 'pot.loc', 'pot.host')

@@

  mod.ext.str.prem <- lm(str.ext.prem~type+as.factor(bedbath),
                    data=str.data.ic)
  mod.pot.str.prem <- lm(str.pot.prem~type+as.factor(bedbath),
                    data=str.data.ic)

  mod.ext.loc.prem <- glm(str.ext.pref~type+as.factor(bedbath)+
                                  sub.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.loc.prem <- glm(str.pot.pref~type+as.factor(bedbath)+
                                  sub.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)

  mod.ext.host.prem <- lm(str.ext.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)

    prem.models <- list(mod.ext.str.prem, mod.ext.loc.prem, mod.ext.host.prem, 
                      mod.pot.str.prem, mod.pot.loc.prem, mod.pot.host.prem)
    names(prem.models) <- c('ext.str', 'ext.loc', 'ext.host',
                          'pot.str', 'pot.loc', 'pot.host')

@@

  mod.pot.ps <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[ps,])

  mod.pot.os <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[os,])

  mod.pot.mu <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[mu,])

  mod.pot.un <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[un,])

  mod.ext.ps <- glm(str.ext.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[ps,])

  mod.ext.os <- glm(str.ext.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[os,])

  mod.ext.mu <- glm(str.ext.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[mu,])

  mod.ext.un <- glm(str.ext.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[un,])

host.models <- list(mod.ext.ps, mod.ext.os, mod.ext.mu, mod.ext.un,
                    mod.pot.ps, mod.pot.os, mod.pot.mu, mod.pot.un)
names(host.models) <- c('ext.ps', 'ext.os', 'ext.mu', 'ext.un',
                        'pot.ps', 'pot.os', 'pot.mu', 'pot.un')

@@

pra.coef <- extrMWLCoef(pot.results.all,
                        est.points,
                        x.names)
era.coef <- extrMWLCoef(ext.results.all,
                        est.points,
                        x.names)
prp.coef <- extrMWLCoef(pot.results.ps,
                        est.points,
                        x.names)
pro.coef <- extrMWLCoef(pot.results.os,
                        est.points,
                        x.names)
prm.coef <- extrMWLCoef(pot.results.mu,
                        est.points,
                        x.names)
pru.coef <- extrMWLCoef(pot.results.un,
                        est.points,
                        x.names)
erp.coef <- extrMWLCoef(ext.results.ps,
                        est.points,
                        x.names)
ero.coef <- extrMWLCoef(ext.results.os,
                        est.points,
                        x.names)
erm.coef <- extrMWLCoef(ext.results.mu,
                        est.points,
                        x.names)
eru.coef <- extrMWLCoef(ext.results.un,
                        est.points,
                        x.names)
all.mwl.coefs <- list(pra.coef, era.coef, prp.coef, pro.coef, prm.coef, pru.coef,
                  erp.coef, ero.coef, erm.coef, eru.coef)
names(all.mwl.coefs) <- c('pra', 'era', 'prp', 'pro', 'prm', 'pru', 
                          'erp', 'ero', 'erm', 'eru')

@@

erp.surfs <- makeMWLSurfs(erp.coef,
                          est.points)
ero.surfs <- makeMWLSurfs(ero.coef,
                          est.points)
erm.surfs <- makeMWLSurfs(erm.coef,
                          est.points)
eru.surfs <- makeMWLSurfs(eru.coef,
                          est.points)
all.mwl.surfs <- list(pra.surfs, era.surfs, prp.surfs, pro.surfs, prm.surfs, pru.surfs,
                      erp.surfs, ero.surfs, erm.surfs, eru.surfs)
names(all.mwl.surfs) <- c('pra', 'era', 'prp', 'pro', 'prm', 'pru',
                          'erp', 'ero', 'erm', 'eru')
```

save(clean.count, daily.data, listing.data, ltr.data, pref.table, pref.table.wide,
     s.subs, sssubs, str.data, str.data.ic, subs, all.mwl.coefs, all.mwl.surfs,
     core.suburbs, est.points, exch.rate, host.models, pref.models, prem.models,
     file=paste0(data.path, 'analyzed/analyzed_workspace.RData'))
